Audiovisual Analytics Vocabulary and Ontology (AAVO): initial core and example expansion

### 2017-08-21 latex/article.tex
ordered the bib items

% ------------------------------------------------------------------------
\begin{thebibliography}{99}
\fontsize{11}{0}\selectfont
\bibitem[W3C, 2010]{w3cld}
	W3C (2017). LINKED DATA CURRENT STATUS, from \url{https://www.w3.org/standards/techs/linkeddata}

@@

\bibitem[Fabbri, 2017]{enhance}
	Fabbri, R. (2017). Necessary enhancements of linked data expressiveness for ontologies.
		Encontro Nacional de Modelagem Computacional 2017 (XX ENMC).
		From \url{https://github.com/ttm/ontologyEnhancements/raw/master/article.pdf}

@@

\bibitem[Fabbri \& Oliveira, 2016]{losd}
	Fabbri, R., \& de Oliveira, O. N. (2016). Linked Open Social Database. Github repositories, from \url{https://github.com/ttm/linkedOpenSocialDatabase/raw/master/paper.pdf}

\bibitem[Fabbri, 2017]{fabbri1}
Fabbri, R. (2017). Topological stability and textual differentiation in human interaction networks:
		statistical analysis, visualization and linked data. Doctoral thesis.
		From \url{https://github.com/ttm/thesis/raw/master/thesis-rfabbri.pdf}

\bibitem[Fabbri, 2014]{pnud5}
Fabbri, R. (2014). Social participation ontologies and rules to fuel a social participation linked data cloud.
	Technical report for the United Nations Development Program.
		From \url{https://github.com/ttm/pnud5/raw/master/latex/produto.pdf}

\bibitem[Fabbri et al., 2015]{ops}
Fabbri, R., de Luna, R. B., Martins, R. A. P., Amanqui, F. K. M., \& Moreira, D. D. A. (2015). Social Participation Ontology: community documentation, enhancements and use examples. arXiv preprint arXiv:1501.02662.

\bibitem[Hitzler \& Janowicz, 2013]{semApr}
Hitzler, P., \& Janowicz, K. (2013). Linked Data, Big Data, and the 4th Paradigm. Semantic Web, 4(3), 233-235.

>>>>

% ------------------------------------------------------------------------
\begin{thebibliography}{99}
\fontsize{11}{0}\selectfont
\bibitem[Fabbri, 2017]{enhance}
	Fabbri, R. (2017). Necessary enhancements of linked data expressiveness for ontologies.
		Encontro Nacional de Modelagem Computacional 2017 (XX ENMC).
		From \url{https://github.com/ttm/ontologyEnhancements/raw/master/article.pdf}

@@

\bibitem[W3C, 2010]{w3cld}
	W3C (2017). LINKED DATA CURRENT STATUS, from \url{https://www.w3.org/standards/techs/linkeddata}

@@
